R Notebook

### 2017-04-05 doc/RMD/MLG-distribution.Rmd
add quiet statement

```{r}
setPop(dat) <- ~Region
dat
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
genotype_curve(dat, sample = 1000)
locus_table(dat)
# rl <- fix_replen(dat, repeat_lengths)
# mlg.filter(dat, distance = bruvo.dist, replen = rl) <- .Machine$double.eps
dat
genotype_curve(dat[loc = keeploci, mlg.reset = TRUE])
# dat <- dat[loc = keeploci, mlg.reset = TRUE]
dat
```

>>>>

```{r}
setPop(dat) <- ~Region
dat
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
genotype_curve(dat, sample = 1000, quiet = TRUE)
locus_table(dat)
# rl <- fix_replen(dat, repeat_lengths)
# mlg.filter(dat, distance = bruvo.dist, replen = rl) <- .Machine$double.eps
dat
genotype_curve(dat[loc = keeploci, mlg.reset = TRUE], quiet = TRUE)
# dat <- dat[loc = keeploci, mlg.reset = TRUE]
dat
```
